### 2017-04-06 paper/evaluation.tex
another pass on rq5

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
The goal of the first two questions is to identify potential
discrepancies between the environment used to obtain our results and
the environment of developers.  Overall, we found that \Fix{...}

\Mar{... estou trabalhando neste texto ...}

Based on the answers from developers, we confirmed that most of the
subjects execution time was compatible with the results found at
Section~\ref{sec:rqA}.

\Fix{revise...} From Question I, we noticed that \emailsCI{}
developers confirmed the use of an continuous integration server to
run tests, which \emailsDistributed{} of them is using a distributed
continuous integration server as an alternative to parallelism.
From a local development, \emailsLocal{} developers answered that they
run tests in a local machine, and \emailsNotDescribed{} developers did
not described their environment.

Considering question 2, we found that \emailsSequential{} of the
\emailsProjectsAnswered{} projects indeed did not execute tests in
parallel.  The discrepancy is justified by cases where neither of our
checks (static or dynamic) could detect presence of parallelism.  \Fix{elaborate}

%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.

>>>>

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
%% One of the goals of the first questions is to identify potential
%% discrepancies between our experimental environment and the environment
%% of developers.  Overall, we found that \Fix{...}

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites were modularized and
those modules were tested independetly in CI servers through different
parameters. A total of \emailsLocal{} participants answered that they
do run tests in their local machines.  Note that CI does not preclude
low-level parallelization.  For example, installations of open-source
CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated servers will
still benefit from running tests faster, using test suite
parallelization.

% \emailsNotDescribed{} developers did not described their environment.

Considering question 2, we found that \emailsSequential{} of the
\emailsProjectsAnswered{} projects indeed did not execute tests in
parallel.  The mismatch is justified by cases where neither of our
checks (static or dynamic) could detect presence of parallelism.  \Fix{elaborate}
\Luis{i looked at those 6 weird projects, and 1 of them contains a
false-negative from rq4, one of them considered the distributed CI
server as parallelism, 2 of them had a custom test runner, and 2 of
them implements parallelism inside the test (they test two+ things in
one test method.}
%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.
